|

### 2021-08-11 paper/memo/memo.Rmd
updating memo

The understand of democracy problem could be "misunderstanding" in both authoritarian countries and democratic countries. 
In democracies, the "misunderstanding" is related to another issue which should attract more theoretical discussion, that is, the choice between generic support for democracy and other values especially in the long built democracies [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].
The disparity between the public's generic support and their commitment to support lends light to the recent democracy crisis and the uprising of populism witnessed in well-developed democracies.

<!--
thanks to reviewer2's comments on random walk, we do think we should discuss more on problems caused by random walk, which actually provides us another powerful explanation for our results. 
In terms of the impact of measurement error on estimated effects, many studies have shown that when taking measurement uncertainty into account, the magnitude of coefficients of latent variables can be either attenuated or enlarged substantively [e.g., @Treier2008, p. 211; @caughey2018,p. 254]. -->

>>>>

Thanks to reviewer2's comments on random walk, we do think we should discuss more on problems caused by random walk, which actually provides us another powerful explanation for our results.
In order to isolate the effect of different priors on estimated measures, in revised version, we only employed Claassen's Model5 with original data, recollected data and expanded data, separately.
A bigger size of observed data is expected to reduce the possible dominance of priors.
However, even though we put efforts to collect as much data as possible.
The expanded data is only xxx county-year.
It is possible that the changes of public mood are "smooth" out by modeling the temporal evolution in a simple local-level dynamic linear.
The smoothed time series data might fail to capture a sudden change which is caused by exogenous factors.
Given the sparsed available data and effects from random walk prior, it is highly possible that we cannot detect any significant effect from institution changes and other economic and social factors.
Futhermore, scholars should be careful of using estimated latent variable as a dependent variable when source data is sparsed.
We are planning to carry out more work on figuring out at what rate the sparseness of source data will post severe problems in statistical inference, which will faciliate scholars' usage of latent variable measures.

In terms of the impact of measurement error on estimated effects, as we illustrated in Appendix, point estimates of coefficients are calculated from samples drawn from joint distribution of estimated latent variable and coefficients, which incorporate both uncertainty in latent variable measurements and the relationship between outcome variables and covariates.
Given the big uncertainty in two parts, we should expect the estimated effects are different from point estimates from models without accounting uncertainty. 
Many studies have already shown that when taking measurement uncertainty into account, the magnitude of coefficients of latent variables can be either attenuated or enlarged substantively [e.g., @Treier2008, p. 211; @caughey2018,p. 254].
